\LARGE Tailoring Differentially Private Bayesian Inference to Distance Between Distributions

### 2018-10-13 TPDP2018/poster/main.tex
update poster and plots

\begin{block}{Differentially private Bayesian inference}
\begin{columns} % Subdivide the first main column
  \begin{column}{.69\textwidth}
    \vspace{-3cm}
\begin{itemize}
\item  Baseline approach: 
  \begin{itemize}
  \item Release $\betad(\alpha +  \lfloor\widetilde{\Delta \alpha}\rfloor^n_0,\beta + n - \lfloor\widetilde{\Delta \alpha}\rfloor^n_0)$,
  \item $\widetilde{\Delta \alpha}\sim \lap{\Delta\alpha}{\frac{S}{\epsilon}}$
  \item \todo{$S\propto ||\cdot ||_{1}$}.
  \item Measure accuracy with a metric over distributions, e.g. $\hellinger$.
  \end{itemize}
  \end{itemize}
  {\color{red}{But $S$ grows linearly with the dimension: too noisy when we generalize to Dirichlet-Multinomial ({\small$\dirichlet(\cdot)$}) model}}.
\end{column}
\begin{column}{.28\textwidth}
\begin{figure}[ht]
\centering
\includegraphics[width=0.9\textwidth]{poster_0.eps}
\caption{\footnotesize{Sensitivity of $\hellinger$. There is a gap between Global and Local sensitivity.}}
\label{fig_sensitivity}
\end{figure}
% \vspace{.1cm}
\end{column}
\end{columns}
    \vspace{-1cm}
\begin{itemize}
\item Another approach:
  \begin{itemize}
    \item Calibrate  noise w.r.t \emph{global} sensitivity of $\hellinger$: {\color{red}{but global sensitivity is still too big.}}
    \item Fig. \ref{fig_sensitivity} shows that there is a gap between global and local sensitivity of $\hellinger$.
    \end{itemize}
  \item A better approach:
    \begin{itemize}
      \item \large{Calibrate noise w.r.t. the \emph{smooth} sensitivity of $\hellinger$.}
    \end{itemize}
\end{itemize}

@@

  \begin{block}{Preliminary experimental results}
    Experiments are about three mechanisms and plotted as follows:
\begin{itemize}
  \item {\textbf{\color{green}{Green}}}: Baseline approach. %adds noise scaled to sensitivity proportional to dimensionality,
  \item {\textbf{\color{red}{Red}}}: Improved baseline approach with sensitivity 1 in 2 dimensions and 2 in higher dimensions.
    Indeed: the number of elements in every bin always sums up to $n$ and hence $||\bysinfer(x)-\bysinfer(x')||_1\leq 2$, when $\adj{x}{x'}$.

  \item {\textbf{\color{blue}{Blue}}}: $\hexpmech$. The fact that there is only one candidate distribution which achieves the highest score and different
    distributions which achieve a sub-optimal score explains the (highest) peaks in Fig.  \ref{subfig_concrete_prob_2d} (and Fig. \ref{subfig_concrete_prob_3d}).
\end{itemize}
% In Fig. \ref{subfig_concrete_prob_2d} and \ref{subfig_concrete_prob_3d} we plot on the x-axis the Hellinger distance from the true posterior and on the y-axis the
% probability of the distributions with that distance under the different mechanisms. In Fig. \ref{subfig_prior} we present the influence of the prior on the accuracy of the three mechanisms,
% by showing the quartiles of the experimental distribution of the Hellinger distance.
\begin{figure}[H]
\begin{center}
\centering
  \subfigure[2 dimensions with data size $600$]{
    \includegraphics[width=0.31\textwidth]{poster_5.eps}
  \label{subfig_concrete_prob_2d}
  }
  \subfigure[3 dimensions with data size $600$]{
    \includegraphics[width=0.31\textwidth]{poster_6.eps}
  \label{subfig_concrete_prob_3d}
  } 
\subfigure[2 dimensions with data size $100$]{
    \includegraphics[width=0.313\textwidth]{poster_4.eps}
  \label{subfig_prior}
  }

% \caption{4-quantile and discrete probability plots}
% \label{fig_concrete_prob}
% \end{center}
% \end{figure}
% % Two groups of experimental results both with unit prior $\betad(1,1), \betad(1,1,1)$ and $\betad(1,1,1,1)$, balanced datasets and parameters $\epsilon = 1.0$ and $\delta = 10^{-8}$.
%   Fig. \ref{fig_sampling} and Fig. \ref{subfig_prior} give us the average and 4-quantile of Hellinger distance between the sampled results and true posterior.
% \begin{figure}[H]
% \begin{center}
% \centering
  \subfigure[\footnotesize{2 dimensions, data size $\in [100,500]$}]{
    \includegraphics[width=0.333\textwidth]{poster_1.eps}
    \label{subfig_sampling_2d}
  }
  \subfigure[\footnotesize{3 dimensions, data size $\in [100,500]$} ]{
    \includegraphics[width=0.302\textwidth]{poster_2.eps}
  \label{subfig_sampling_3d}
  } 
  \subfigure[\footnotesize{4 dimensions, data size $\in [100,600]$}]{
    \includegraphics[width=0.295\textwidth]{poster_3.eps}
    \label{subfig_sampling_4d}
  }
  \caption{Priors are $\betad(1,1), \dirichlet(1,1,1)$ and $\dirichlet(1,1,1,1)$ (except for Figure \ref{subfig_prior}) ,
    balanced datasets, $\epsilon = 1.0$ and $\delta = 10^{-8}$. }
\label{fig_sampling}
\end{center}

@@

\begin{itemize}
  \item  $\hexpmech$ outperforms the baseline approach but not the improved one.
  \item By increasing the prior parameters, $\hexpmech$ can outperform both the baseline approach and the improved one.
  % \begin{itemize}
  %   \item  The accuracy that we are going to explore next, and in a more principled and formal way.

>>>>

\begin{block}{Differentially private Bayesian inference}
\begin{columns} % Subdivide the first main column
  \begin{column}{.69\textwidth}
    \vspace{-3cm}
\begin{itemize}
\item  Baseline approach: 
  \begin{itemize}
  \item Release $\betad(\alpha +  \lfloor\widetilde{\Delta \alpha}\rfloor^n_0,\beta + n - \lfloor\widetilde{\Delta \alpha}\rfloor^n_0)$,
  \item $\widetilde{\Delta \alpha}\sim \lap{\Delta\alpha}{\frac{\Delta \bysinfer}{\epsilon}}$
  % \item \todo{$S\propto ||\cdot ||_{1}$}.
  \item $\Delta \bysinfer \equiv \max\limits_{\dataobs, \dataobs' \in \{0,1\}^{n}, ||\dataobs - \dataobs'||_1 \leq 1} ||\bysinfer(\dataobs) - \bysinfer(\dataobs')||_1$
  \item Measure accuracy with a metric over distributions, e.g. $\hellinger$.
  \end{itemize}
  \end{itemize}
  {\color{red}{But $\Delta \bysinfer$ grows linearly with the dimension: too noisy when we generalize to Dirichlet-Multinomial ({\small$\dirichlet(\cdot)$}) model}}.
\end{column}
\begin{column}{.28\textwidth}
\begin{figure}[ht]
\centering
\includegraphics[width=0.9\textwidth]{poster_0.eps}
\caption{\footnotesize{Sensitivity of $\hellinger$. There is a gap between Global and Local sensitivity.}}
\label{fig_sensitivity}
\end{figure}
% \vspace{.1cm}
\end{column}
\end{columns}
    \vspace{-1cm}
\begin{itemize}
\item Another approach:
  \begin{itemize}
    \item Calibrate  noise w.r.t \emph{global} sensitivity of $\hellinger$: {\color{red}{but global sensitivity is still too big.}}
    \item Fig. \ref{fig_sensitivity} shows that there is a gap between global and local sensitivity of $\hellinger$.
    \end{itemize}
  \item A better approach:
    \begin{itemize}
      \item \large{Calibrate noise w.r.t. the \emph{smooth} sensitivity of $\hellinger$.}
    \end{itemize}
\end{itemize}

@@

  \begin{block}{Preliminary experimental results}
    Experiments are about three mechanisms and plotted as follows:
\begin{itemize}
  \item {\textbf{\color{green}{Green}}}: Baseline approach. %adds noise scaled to sensitivity proportional to dimensionality,
  \item {\textbf{\color{red}{Red}}}: Improved approach by using sensitivity 1 in 2 dimensions and 2 in higher dimensions.
    Indeed: we can see the output of the Bayesian inference as a histogram, so the $||\bysinfer(\dataobs)-\bysinfer(\dataobs')||_1 \leq 2$.

  \item {\textbf{\color{blue}{Blue}}}: $\hexpmech$. The fact that there is only one candidate distribution which achieves the highest score and different
    distributions which achieve a sub-optimal score explains the (highest) peaks in Fig.  \ref{subfig_concrete_prob_2d} (and Fig. \ref{subfig_concrete_prob_3d}).
\end{itemize}
% In Fig. \ref{subfig_concrete_prob_2d} and \ref{subfig_concrete_prob_3d} we plot on the x-axis the Hellinger distance from the true posterior and on the y-axis the
% probability of the distributions with that distance under the different mechanisms. In Fig. \ref{subfig_prior} we present the influence of the prior on the accuracy of the three mechanisms,
% by showing the quartiles of the experimental distribution of the Hellinger distance.
\begin{figure}[H]
\begin{center}
\centering
  \subfigure[2 dimensions with data size $600$]{
    \includegraphics[width=0.31\textwidth]{poster_5.eps}
  \label{subfig_concrete_prob_2d}
  }
  \subfigure[3 dimensions with data size $600$]{
    \includegraphics[width=0.31\textwidth]{poster_6.eps}
  \label{subfig_concrete_prob_3d}
  } 
\subfigure[2 dimensions with data size $100$]{
    \includegraphics[width=0.313\textwidth]{poster_6.eps}
  \label{subfig_prior}
  }

  % \subfigure[\footnotesize{2 dimensions, data size $\in [100,500]$}]{
  %   \includegraphics[width=0.333\textwidth]{poster_1.eps}
  %   \label{subfig_sampling_2d}
  % }

  \subfigure[2 dimensions with data size $100$]{
    \includegraphics[width=0.313\textwidth]{poster_4.eps}
  \label{subfig_prior}
  }
  \subfigure[\footnotesize{3 dimensions, data size $\in [100,500]$} ]{
    \includegraphics[width=0.302\textwidth]{poster_2.eps}
  \label{subfig_sampling_3d}
  } 
  \subfigure[\footnotesize{4 dimensions, data size $\in [100,600]$}]{
    \includegraphics[width=0.295\textwidth]{poster_3.eps}
    \label{subfig_sampling_4d}
  }
  \caption{Priors are $\betad(1,1), \dirichlet(1,1,1)$ and $\dirichlet(1,1,1,1)$ (except for Figure \ref{subfig_prior}) ,
    balanced datasets, $\epsilon = 1.0$ and $\delta = 10^{-8}$. }
\label{fig_sampling}
\end{center}

@@

\begin{itemize}
  \item  $\hexpmech$ outperforms the baseline approach but not the improved one.
  \item By increasing the priors parameter, we can be comparable to the improved one.
  % \begin{itemize}
  %   \item  The accuracy that we are going to explore next, and in a more principled and formal way.
